Flexibility of interactions depends on habitat suitability

### 2019-07-09 paper/draft-info.Rmd
Update draft info

* Should I include more networks? Easy to get some more from other published studies. Could improve the manuscript but every new data set has to be cleaned independently and might take one to half a day per network.
* Should I increase the resolution of the bioclimatic variables? Currently working with 2.5' (~5km). Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now.

@@

* Downloaded network data from the Web of Life and cleaned it. I didn't anticipated data needed SO MUCH work! I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do. Quite a mess...
* Downloaded bioclimatic and habitat data

>>>>

* Should I include more networks? Easy to get some more from other published studies. Could improve the manuscript but every new data set has to be cleaned independently and might take one to half a day per network.
* Should I increase the resolution of the bioclimatic variables? Currently working with 2.5' (~5km). Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now. 
* Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})

@@

* Downloaded network data from the Web of Life and cleaned it. I didn't anticipated data needed SO MUCH work! I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do. Quite a mess...
* Downloaded bioclimatic and habitat data
* Dowloaded species occurrences. Wasn't straightforward as there is a lot of species and lots of restrictions with the GBIF API. About a week getting this to work.

### 2019-07-09 paper/manuscript.Rmd
Update draft info

We retrieved occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
For each species, we downloaded occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` of the species of interest. 
The occurrences obtained contain observations of mixed quality, so we applied a series of simple filters to remove those of lower quality. 
Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref? or why?); (*iii*) those in which the number of individuals recorded was either zero or more than 100 as such large counts are often erroneous (ref? or why?); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (ref? why?). 
We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences. 
We removed occurrences in which their coordinates (*v*) fell outside the borders of the country in which they were recorded; (*vi*) those arround a the country capital or the centroid of the country and province centroids; (*vii*) those arond a biodiversity institution; and (*viii*) those located within oceans. 
Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species.

>>>>

We retrieved occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
For each species, we downloaded occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` of the species of interest. 
The occurrences obtained contain observations of mixed quality, so we applied a series of simple filters to remove those of lower quality. 
\R{rationale-occurrence-filtering}Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref? or why?); (*iii*) those in which the number of individuals recorded was either zero or more than 100 as such large counts are often erroneous (ref? or why?); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (ref? why?). 
We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences. 
We removed occurrences in which their coordinates (*v*) fell outside the borders of the country in which they were recorded; (*vi*) those arround a the country capital or the centroid of the country and province centroids; (*vii*) those arond a biodiversity institution; and (*viii*) those located within oceans. 
Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species.
